\textbf{Predicting virus-receptor mutant binding by molecular dynamics simulation}

### 2013-06-20 paper.tex
Copy edits and final changes before sending back... second.

Although our computational predictions largely agreed with the available literature, some mutations that are reported to cause reduced infectivity in experimental systems (most notably vArg111Ala and Asn348Lys, discussed above) were indistinguishable from the WT complex in our simulations. We would like to emphasize here that we cannot expect perfect agreement. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. It is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). In addition, the available experimental data for the GP1/hTfR1 system were generally obtained from infection assays, not binding assays. There are several reasons other than binding due to which a viral mutation may cause a phenotypic difference in infectivity. First, from infectivity experiments it is not clear the extent to which a protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique may further clarify large-scale folding differences. Second, since we start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) would be underestimated by our method. Third, although it is tempting to think diminished infectivity should correlate strongly with decreased binding affinity, it is likely that dramatically increased binding affinity would prohibit cellular membrane detachment after viral invasion. As a result, the virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.

>>>>

Although our computational predictions largely agreed with the available literature, some mutations that are reported to cause reduced infectivity in experimental systems (most notably vArg111Ala and Asn348Lys, discussed above) were indistinguishable from the WT complex in our simulations. We would like to emphasize here that we cannot expect perfect agreement. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. It is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). In addition, the available experimental data for the GP1/hTfR1 system were generally obtained from infection assays, not binding assays. There are several reasons other than binding due to which a viral mutation may cause a phenotypic difference in infectivity. First, from infectivity experiments it is not clear the extent to which a protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique may further clarify large-scale folding differences. Second, since we start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) would be underestimated by our method. Third, it is tempting to think only decreased binding affinity should correlate strongly with diminished infectivity. However, dramatically increased binding affinity would also disrupt infectivity by prohibiting cellular membrane detachment after viral invasion. The virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.
